A Novel Sampling Method Using Stochastic Gradient Descent

### 2016-12-07 paper/main.tex

% ===================================================================================
\section{Discussion} % (fold)
\label{sec:discussion}
In this paper, we rediscovered Langevin SGD-based sampler and researched on its stationary distribution, mixing time, and how to use it to do posterior sampler. 
\begin{enumerate}
    \item When the objective of SGD is chosen to be $\log f(x)$, the stationary distribution is approximately the same as $f(x)$. Empirical simulation shows even if $f(\cdot)$ has two modes, SGD sampler will still reach a pretty accurate distribution.
    \item When sampling from a posterior distribution, the SGD update step can be estimated using a randomly chosen subset of the whole dataset. A toy example of estimating the expectation and variance of a Gaussian distribution demonstrate its performance.
    \item We also carried out a comparison between SGD's mixing time and its convergence time. Empirical simulations show that when SGD converges fast, it will also have a small mixing time.
\end{enumerate}
Future work includes:
\begin{enumerate}
    \item we will dig into the literature on Langevin MCMC and learn more about this issue. 
    \item Current analysis cannot apply to the multiple-mode distribution. The simple simulation showed SGD, although very slow, still works in that case. Thus we might be able to consider this scenario in the future.
    \item The mixing time of SGD based sampling will be prohibitively large when multiple modes are present. We would also like to consider how to overcome this issue.
\end{enumerate}

>>>>

% ===================================================================================
\section{Discussion} % (fold)
\label{sec:discussion}

In this paper, we have shown that stochastic gradient descent approaches extend in an elegant way to a sampler for posterior distributions when computing the likelihood from the full data is intensive. We are able to establish the stationary distribution of the procedure and gave several examples showing the accuracy and uses of our result. By taking a Bayesian route, we are able to show that the SGD algorithm is a sampler of a posterior under a non-informative prior. This enables us to establish connection between SGD and maximum \emph{a posteriori} (MAP) procedure, which is an analogy to gradient descent solving a maximum likelihood estimator in the frequentist paradigm. A natural extension of this work, which we hope to be able to accomplish, is to derive finite sample rates of convergence for the mixing time, which would allow a more rigor understanding of the SGD family as a whole. Extensive simulation of the methodology is also needed to fully understand this novel SGD sampler.

A detailed contribution is summarized as the following:
\begin{enumerate}
    \item When the objective of SGD is chosen to be $\log f(x)$, the stationary distribution is approximately the same as $f(x)$. Empirical simulation shows even if $f(\cdot)$ has two modes, SGD sampler will still reach a pretty accurate distribution.
    \item When sampling from a posterior distribution, the SGD update step can be estimated using a randomly chosen subset of the whole dataset. A toy example of estimating the expectation and variance of a Gaussian distribution demonstrate its performance.
    \item We also carried out a comparison between SGD's mixing time and its convergence time. Empirical simulations show that when SGD converges fast, it will also have a small mixing time.
\end{enumerate}
Future work includes:
\begin{enumerate}
    \item we will dig into the literature on Langevin MCMC and learn more about this issue. 
    \item Current analysis cannot apply to the multiple-mode distribution. The simple simulation showed SGD, although very slow, still works in that case. Thus we might be able to consider this scenario in the future.
    \item The mixing time of SGD based sampling will be prohibitively large when multiple modes are present. We would also like to consider how to overcome this issue.
\end{enumerate}
